---
title: "KISTERSFishTemplate"
author: "Catarina Pien"
date: "6/15/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load libraries
```{r load }
library(dplyr)
library(tidyr)
library(ggplot2)
library(lubridate)
library(anytime)
library(stringr)
```

Import data
```{r importdata}

# Data retrieved 6/15/2020
# Revised: 7/22/2021
fish_catch1 <- read.csv("Data/Catch1.csv")
fish_catch2 <- read.csv("Data/Catch2.csv")
fish_catch3 <- read.csv("Data/Catch3.csv")
fish_catch4 <- read.csv("Data/Catch4.csv")
fish_catch5 <- read.csv("Data/Catch5.csv")
fish_catchM1 <- rbind(fish_catch1, fish_catch2)
fish_catchM2 <- rbind(fish_catchM1, fish_catch3)
fish_catchM3 <- rbind(fish_catchM2, fish_catch4)
fish_catchM <- rbind(fish_catchM3, fish_catch5)
fish_stations <- read.csv("Data/YBFMP_Stations_Coordinates_info.csv")
fish_ref <- read.csv("Data/Sample_20210722.csv")
fish_tax <- read.csv("Data/FishLookUp.csv")
fish_tax_ed <- read.csv("Data/FishTaxonomyKISTERS.csv") #Edited for KISTERS, only has species present
smelt_gen <- read.csv("Data/SmeltGenetics_20210722.csv")
salm_gen <- read.csv("Data/SalmGenetics_20210722.csv")
salm_diet1 <- read.csv("Data/SalmonDiet_2012_2015.csv")
salm_diet2 <- read.csv("Data/SalmonDiet_2016.csv")
salm_diet3 <- read.csv("Data/SalmonDiet_2017.csv")
salm_diet4 <- read.csv("Data/SalmonDiet_2018.csv")
smelt_diet <- read.csv("Data/SmeltDiets.csv")
seine <- read.csv("Data/SeineEffort_20210722.csv")
trap <- read.csv("Data/TrapEffort_20210722.csv")
cwt <- read.csv("Data/CWT_20210722.csv")
stationNum <- read.csv("Data/YBFMP_Stations_Coordinates_Info.csv")
str(fish_ref)

# Add and change date formats
#fish_ref$SampleTime <- hms(fish_ref$SampleTime)
fish_ref <- mutate(fish_ref, Datetime = paste(SampleDate, SampleTime, sep = " ")) 
fish_ref$Datetime <-  mdy_hms(fish_ref$Datetime) 
fish_ref <- arrange(fish_ref, Datetime)
# fish_ref$Year <- ordered(year(fish_ref$Datetime))
# fish_ref$Month <- ordered(month(fish_ref$DateTime))
fish_ref$SampleDate <-as.Date(fish_ref$SampleDate,format ="%m/%d/%Y")
fish_ref$SampleTime <- parse_date_time(fish_ref$SampleTime, '%I:%M:%S %p')

# Make some lists
dietOrgs <- c("CHN", "RBT", "WAG", "LFS", "DSM")
salmonids <- c("CHN", "RBT")
smelts <- c("DSM", "WAG", "LFS")

str(fish_ref)
```


Clean 
```{r clean}
library(magrittr)

## define a helper function
empty_as_na <- function(x){
    if("factor" %in% class(x)) x <- as.character(x) ## since ifelse wont work with factors
    ifelse(as.character(x)!="", x, NA)
}

# Sample 
fish_ref_clean <- fish_ref %>% 
  select(-c(WeatherCode,MicrocystisVisualRank:s_Lineage)) %>%
  filter(!StationCode %in% c("STB", "STB3", "STB5", "STFP", "YBSP1", "CCS5", "CCS6")) %>%
  mutate(StationCode = replace(StationCode, StationCode == "STS", "BL4"),
         StationCode = replace(StationCode, StationCode == "YBSP1", "YB")) %>%
  mutate(StationCode = replace(as.character(StationCode), StationCode == "LI", "LIS")) %>%
 mutate(MethodCode = replace(MethodCode, MethodCode == "FNET", "FKTR")) %>%
 # mutate()
  rename(SampleMethod = MethodCode)

unique(fish_ref_clean$VegetationRank)
unique(fish_ref_clean$GearConditionCode)
unique(fish_ref_clean$StationCode)
unique(fish_ref_clean$SampleMethod)
unique(fish_ref_clean$GearID)

# Catch
fish_catch_clean <- fish_catch %>%
  filter(!(OrganismCode == "CHN" & Count == 0)) %>%
  select(-c(s_ColLineage:s_Lineage))%>%
  mutate(OrganismCode = ifelse(as.character(OrganismCode) == "lp", "LP", as.character(OrganismCode)),
         OrganismCode = ifelse(as.character(OrganismCode) == "tfs", "TFS", as.character(OrganismCode)),
  OrganismCode = ifelse(as.character(OrganismCode) == "SF", "PKN", as.character(OrganismCode)))  %>%
  rename(FishIDComments = Comments) %>%
  mutate(Plus.Count = replace(Plus.Count, is.na(ForkLength) & Count >1, TRUE),
         Plus.Count = replace(Plus.Count, !is.na(ForkLength) & Count == 1, FALSE)) %>%
  mutate(Race = ifelse(Race == "f", "F",
                       ifelse(Race == "U" | Race == "", "n/p", as.character(Race)))) %>%
  mutate(Sex = ifelse(Sex == "Female", "F",
                      ifelse(Sex == "Male", "M",
                             ifelse(Sex == "Unknown", "U", NA)))) %>%
  mutate(FishTagID = str_replace_all(FishTagID, "2019Ad_Plus", "2019Ad_plus")) %>%
  mutate(MarkCode = replace(MarkCode, MarkCode == "none", "None")) %>%
  mutate(Spawning.Condition = ifelse(Spawning.Condition == 
                                       "Expressing Eggs", "EGGS",
                                     ifelse(Spawning.Condition == "Expressing Milt", "MILT",
                                            NA))) %>%
  mutate(StageCode = ifelse(StageCode == "CHN_S", "SMT", 
                           ifelse(StageCode == "CHN_P", "PAR",
                                  ifelse(StageCode == "CHN_X", "TRS", 
                                         ifelse(substring(FishTagID, 1L, 1L) == "A", "ADT",
                                                ifelse(StageCode == "n/p", "n/p",
                                                NA))))))
fish_catch_clean$FishTagID <- gsub("minus", "min", fish_catch_clean$FishTagID)
fish_catch_clean$FishTagID <- gsub("min", "minus", fish_catch_clean$FishTagID)

empty <- filter(fish_catch_clean, is.na(SampleID)) 

unique(fish_catch_clean$MarkCode)
unique(fish_catch_clean$StageCode) ### Check if there are changes
unique(fish_catch_clean$Spawning.Condition)
unique(fish_catch_clean$Sex)
unique(fish_catch_clean$Race)
a <- filter(fish_catch_clean, Race == "n/p" & OrganismCode == "CHN")

#51 Observations without SampleID. 

# Taxa
fish_tax_clean <- fish_tax %>%
  select(c(2,4)) %>%
  dplyr::rename(Field_ID_CommonName = CommonName)

fish_tax_ed_clean <- fish_tax_ed %>%
  dplyr::rename(OrganismCode = OrganismCode_FISH,
                Field_ID_CommonName = CommonName)

# Seine
seine_clean <- seine %>%
  select(c(1, 4:10, 11, 16)) %>%
  rename(SeineComments=Comments) %>%
  mutate(SubstrateCode =
           ifelse(as.character(SubstrateCode) %in% c("Gravel", "grv", "GR"),
             "GRV",
             ifelse(as.character(SubstrateCode) %in% c("Mud", "MD", "md", "mud"),
               "MUD",
               ifelse(as.character(SubstrateCode) %in% c("PV", "Pavement"),
                 "PAV",
                 ifelse(as.character(SubstrateCode) %in% c("Vegetation", "VG"),
                   "AVG",
                   ifelse(as.character(SubstrateCode) %in% c("Sand", "SN", "silt"),
                     "SND",
                     ifelse(as.character(SubstrateCode) == "mud and gr",
                       "GRV",
                       ifelse(as.character(SubstrateCode) == "mud/veg",
                         "AVG",
                         ifelse(as.character(SubstrateCode) == "grass", 
                           "TVG",
                     as.character(SubstrateCode)
                   )))))))))
         

unique(seine_clean$HabitatType) #good
unique(seine_clean$SubstrateCode) # good
unique(seine_clean$Region)

# Trap
trap_clean <- trap %>%
  select(1, 4:6) %>%
  rename(TrapComments = Comments)

unique(trap_clean$TrapStatus)

## genetics ##
smelt_gen_clean <- smelt_gen %>%
  select(-c("Active")) %>%
  dplyr::rename(GenotypeRun = Genotype.Run,
                GeneticID = SPECIES..Assay.ID.,
                qDS = q..DS.,
                qLFS = q..LF.,
                qWAG = q..WK.,
                numChrom = X..Chroms,
                SmeltComments = COMMENTS)%>%
  mutate(GeneticID = ifelse(GeneticID == "hybrid (LFS/WAG)", "HYB_LFS_WAG",
                            ifelse(GeneticID == "hybrid (DSM/WAG)", "HYB_DSM_WAG",
                                   ifelse(GeneticID == "missing data", "UNK", as.character(GeneticID)))))

unique(smelt_gen_clean$GeneticID)
unique(smelt_gen_clean$V.shape)

salm_gen_clean <- salm_gen %>%
  dplyr::rename(GeneticID1 = BestEstimate,
                GeneticID2 = X2ndBestEstimate,
                SalmComments = Comments) 
salm_gen_clean$FishTagID <- gsub("minus", "min", salm_gen_clean$FishTagID)
salm_gen_clean$FishTagID <- gsub("min", "minus", salm_gen_clean$FishTagID)


# CWT
cwt_clean <- cwt %>%
  select(-CWTRowID) %>%
  rename(CWTComments = Comments)

# Station Number
staNum_clean <- stationNum %>%
  select(c(1,2)) %>%
  rename(StationCode = Station.Name) 
```

Diet data
```{r diet}

# Salmon Diet

salm_diet <- read.csv("Data/SalmonDiet_2012_2015.csv")
diets2016 <- read.csv("Data/SalmonDiet_2016.csv")
diets2017 <- read.csv("Data/SalmonDiet_2017.csv")
diets2018 <- read.csv("Data/SalmonDiet_2018.csv")
smelt_diet <- read.csv("Data/SmeltDiets.csv")

salm_diet_c1 <- dplyr::rename(salm_diet,
       ProcessedBy = Processed.by,
       FishTagID = ID..,
       ForkLength = FL,
       ForkLengthLabel = FL..Label.if.different.from.data.sheet.,
       WeightLabel = Label.Weight..If.does.not.match.weight.on.Inventory.,
       SampleDate = Date,
       StationCode = Site.Code,
       Race = X,
       WeightStomachFull = Damp.wt,
       WeightStomachEmpty = Empty.wt,
       PreyTaxa = Prey.taxa,
       WeightPrey = Wt,
       LifeStage = LH,
       StomachBrokenDamaged = Stomach.broken.damaged,
       ProcessedBy = Processed.by,
       StomachComments = Comments,
       HigherTaxa = REF,
       QAQCBy = QA) %>%
  mutate(OrganismCode = "CHN",
         SN = NA,
         SampleTime = NA) %>%
 select(c("FishTagID", "SampleDate", "SampleTime", "StationCode", "Gear", "OrganismCode", "SN", "Race", "ForkLength", "Weight", "ForkLengthLabel", "WeightLabel", "Fullness", "Digestion", "WeightStomachFull", "WeightStomachEmpty", "PreyTaxa", "LifeStage", "HigherTaxa", "Count", "WeightPrey", "StomachBrokenDamaged", "StomachComments", "ProcessedBy", "QAQCBy"))


diets2016c <- diets2016 %>%
  rename(
    ProcessedBy = Processed.by,
    FishTagID = ID,
    ForkLength = FL..mm.,
    Weight = wt..g.,
    OrganismCode = Species,
    SampleDate = Date,
    SampleTime = Time,
    StationCode = Gear,
    WeightStomachFull = full.wt,
    WeightStomachEmpty = empty.wt,
    PreyTaxa = Prey.Taxa,
    WeightPrey = wt..g..1,
    LifeStage = LH,
    StomachComments = Comments,
    HigherTaxa = Higher.level,
    QAQCBy = QA.QC
  ) %>%
  mutate(Gear = NA,
         Race = NA,
         ForkLengthLabel = NA,
         WeightLabel = NA,
         StomachBrokenDamaged = NA,
         Inventory = NA) %>%
 select(c("FishTagID", "SampleDate", "SampleTime", "StationCode", "Gear", "OrganismCode", "SN", "Race", "ForkLength", "Weight", "ForkLengthLabel", "WeightLabel", "Fullness", "Digestion", "WeightStomachFull", "WeightStomachEmpty", "PreyTaxa", "LifeStage", "HigherTaxa", "Count", "WeightPrey", "StomachBrokenDamaged", "StomachComments", "ProcessedBy", "QAQCBy"))


diets201718 <- rbind(diets2017, diets2018)

diets201718c <-  diets201718 %>%
  rename(
    ProcessedBy = Processed.by,
    FishTagID = ID,
    ForkLength = FL..mm.,
    Weight = wt..g.,
    OrganismCode = Species,
    SampleDate = Date,
    SampleTime = Time,
    WeightStomachFull = full.wt,
    WeightStomachEmpty = empty.wt,
    PreyTaxa = Prey.Taxa,
    WeightPrey = wt..g..1,
    LifeStage = LH,
    StomachComments = Comments,
    HigherTaxa = Higher.level,
    QAQCBy = QA.QC
  ) %>%
  mutate(OrganismCode = ifelse(grepl("DSM", FishTagID), "DSM", 
                               as.character(OrganismCode)),
    StationCode = NA,
    SN = NA,
         Gear = NA,
         Race = NA,
         ForkLengthLabel = NA,
         WeightLabel = NA,
         StomachBrokenDamaged = NA,
    Inventory = NA) %>%
 select(c("FishTagID", "SampleDate", "SampleTime", "StationCode", "Gear", "OrganismCode", "SN", "Race", "ForkLength", "Weight", "ForkLengthLabel", "WeightLabel", "Fullness", "Digestion", "WeightStomachFull", "WeightStomachEmpty", "PreyTaxa", "LifeStage", "HigherTaxa", "Count", "WeightPrey", "StomachBrokenDamaged", "StomachComments", "ProcessedBy", "QAQCBy"))

# salmonid
salm_diet_c2 <- filter(diets2016c, OrganismCode == "CHN" |OrganismCode == "RBT")
salm_diet_c3 <- filter(diets201718c, OrganismCode == "CHN")
salm_diet_clean0 <- rbind(salm_diet_c2, salm_diet_c3)
salm_diet_clean <- rbind(salm_diet_c1, salm_diet_clean0) 
str(salm_diet_clean)
salm_diet_clean$SampleDate <- as.Date(salm_diet_clean$SampleDate, format = "%m/%d/%Y")
salm_diet_clean <- salm_diet_clean %>%
  arrange(SampleDate, FishTagID)
salm_diet_clean$FishTagID <- gsub("_Ad", "Ad", salm_diet_clean$FishTagID)
salm_diet_clean$FishTagID <- gsub("minus", "min", salm_diet_clean$FishTagID)
salm_diet_clean$FishTagID <- gsub("min", "minus", salm_diet_clean$FishTagID)

# smelt 
head(smelt_diet)

smelt_diet_c1 <- dplyr::rename(smelt_diet,
       ProcessedBy = Processed.by,
       FishTagID = ID..,
       ForkLength = FL,
       ForkLengthLabel = FL..Label.if.different.from.data.sheet.,
       WeightLabel = Weight.in.field,
       SampleDate = Date,
       HigherTaxa = X,
       WeightStomachFull = Damp.wt,
       WeightStomachEmpty = Empty.wt,
       PreyTaxa = Prey.taxa,
       WeightPrey = Wt,
       LifeStage = LH,
       StomachBrokenDamaged = Stomach.broken.damaged,
       ProcessedBy = Processed.by,
       StomachComments = Comments,
       QAQCBy = QA) %>%
       mutate(OrganismCode = ifelse(grepl("W", FishTagID), "WAG",
                        ifelse(grepl("S", FishTagID), "DSM", NA)),
         StationCode = NA,
         Race=NA,
         SN = NA,
         Gear = NA,
         SampleTime = NA) %>%
 select(c("FishTagID", "SampleDate", "SampleTime", "StationCode", "Gear", "OrganismCode", "SN", "Race", "ForkLength", "Weight", "ForkLengthLabel", "WeightLabel", "Fullness", "Digestion", "WeightStomachFull", "WeightStomachEmpty", "PreyTaxa", "LifeStage", "HigherTaxa", "Count", "WeightPrey", "StomachBrokenDamaged", "StomachComments", "ProcessedBy", "QAQCBy"))


smelt_diet_c2 <- filter(diets2016c, OrganismCode %in% c("DSM", "WAG")) 
smelt_diet_c3 <- filter(diets201718c, OrganismCode %in% c("DSM", "WAG"))
smelt_diet_clean0 <- rbind(smelt_diet_c2, smelt_diet_c3)
smelt_diet_clean <- rbind(smelt_diet_c1, smelt_diet_clean0)
smelt_diet_clean$SampleDate <- as.Date(smelt_diet_clean$SampleDate, format = "%m/%d/%Y")
smelt_diet_clean <- smelt_diet_clean %>%
    arrange(SampleDate, FishTagID)
smelt_diet_clean$FishTagID <- gsub("2016WAG", "2016_WAG", smelt_diet_clean$FishTagID)
smelt_diet_clean$FishTagID <- gsub("WAG0", "WAG_0", smelt_diet_clean$FishTagID)

diet_clean <- rbind(salm_diet_clean, smelt_diet_clean)
str(diet_clean)

diet_clean$SampleTime <- strptime(diet_clean$SampleTime, format = "%H:%M")
diet_clean$SampleTime <- as.POSIXct(diet_clean$SampleTime, format = "%H:%M")
summary(diet_clean)
```


1. Join catch and genetics, QC
```{r joinGenetics}

### Genetics

CatchGenetics <- left_join(fish_catch_clean, salm_gen_clean, by = "FishTagID")
CatchGenetics2 <- left_join(CatchGenetics, smelt_gen_clean, by = "FishTagID") %>%
    mutate_each(funs(empty_as_na))

# QC Genetics
checkGen <- filter(CatchGenetics2, FishTagID !="" & Genetic.Sample == "TRUE") %>%
  arrange(OrganismCode)

# Salmon
checkGenSalm <- filter(checkGen, is.na(Prob1) & 
                         OrganismCode == "CHN" & 
                         !grepl("2020", FishTagID)  &
                         !grepl("min", FishTagID)) %>%
  arrange(FishTagID)

# Add 2019_ACHN_001
# Add 2017Ad_plus-F_02
# Add all 2019Ad_Plus-S
# Add all 2019Ad_Plus-W

# Smelt 
checkGenSmelt <- filter(checkGen, is.na(GeneticID) & 
                          OrganismCode %in% c("DSM", "LFS", "WAG") & 
                          !grepl("2020", FishTagID) & 
                          is.na(GeneticID)) %>% arrange(FishTagID)

# Add all of this in. I think some are missing. 

# Sent to Amanda
# write.csv(checkGenSalm, "R_write/SalmonMissing2.csv")
# write.csv(checkGenSmelt, "R_write/SmeltMissing2.csv")

```

2. Join CWT, QC
```{r joinCWT}
CatchGenCWT <- left_join(CatchGenetics2, cwt_clean)

checkCWT <- filter(CatchGenCWT, 
                   OrganismCode == "CHN",
                   grepl("min", FishTagID),
                   is.na(CWT_TagCode),
                   !grepl("no tag", CWTComments),
                   !grepl("tag lost", CWTComments)) %>%
  select(-c(SalmGenRowID:GenotypeRun))

# Sent to Amanda missing CWT Tags
# write.csv(checkCWT, "R_write/MissingCWTTag.csv")

```

3. Join with taxonomic info, QC
```{r joinTaxonomy}
CatchTaxon <- left_join(CatchGenCWT, fish_tax_ed_clean) 
checkTaxa <- filter(CatchTaxon, is.na(TaxonName))
```

4. Join Sample info with seine info
```{r joinSampleSeine, warning = FALSE, message = FALSE}

SampleSeine <- left_join(fish_ref_clean, seine_clean) %>%
  mutate(GearConditionCode = ifelse(is.na(GearConditionCode) & !is.na(ConditionCode), ConditionCode, GearConditionCode),
    GearConditionCode = ifelse(grepl("too deep", SeineComments), 4, GearConditionCode),
         GearConditionCode = ifelse(grepl("Too much hyacinth", SeineComments), 4, GearConditionCode)) %>%
  select(-c(ConditionCode))
# Converted comments of no seining to gear condition code of 4. 

checkSampleSeine <- filter(SampleSeine, 
                           SampleMethod == "BSEIN",
                           is.na(VolumeSeined),
                           GearConditionCode!= "4") %>%
  arrange(SampleDate, StationCode)

# Lots of missing seine info (length, width, depth). 

```

5. Join above with trap info
```{r joinTrap, warning = FALSE, message = FALSE}
SampleTrap <- left_join(SampleSeine, trap_clean) %>%
  mutate_if(is.factor, funs(empty_as_na)) %>%
  mutate_if(is.character, funs(empty_as_na)) %>%
  mutate(FieldComments = ifelse(SampleMethod == "BSEIN", SeineComments,
                                ifelse(SampleMethod %in% c("RSTR","FKTR"), TrapComments, NA)))%>%
  select(-c(TrapComments,SeineComments))
  
str(SampleTrap)

checkSampleTrap <- filter(SampleTrap,
                          SampleMethod == "RSTR",
                          GearConditionCode!="4") %>%
  select(-c(SeineLength:VolumeSeined)) %>%
  arrange(SampleDate, StationCode)

```

6. Station Number

```{r joinStation, message = FALSE, warning = FALSE}
StationNum <- left_join(SampleTrap, staNum_clean)

checkStationNum <- filter(StationNum, is.na(Station.Number))

# Deal with stations not on the list 

```

7. Join all

```{r joinAll, warning = FALSE, message = FALSE}
alldata <- full_join(StationNum, CatchTaxon) %>%
  arrange(Datetime, StationCode)

str(alldata)

# Remove anything without a SampleID

alldata <- filter(alldata, !is.na(SampleID))

# Remove some columns
alldata <- alldata %>%
  select(-c(Kingdom:Superfamily, SmeltGenRowID, SalmGenRowID))

alldata$SampleDate <- as.Date(alldata$SampleDate, format = "%m/%d/%Y")

```


8. Join diet data

```{r joinDiet}

#QAQC
salm <- full_join(diet_clean, by = "FishTagID")
checksalmdiet <- salm %>%
  filter(is.na(OrganismCode.y))
uniquesalm <- unique(checksalmdiet$FishTagID) # 296 fish IDs missing in catch table

smelt <- full_join(smelt_diet_clean, CatchGenetics2, by = "FishTagID")
checksmeltdiet <- smelt %>% filter(is.na(OrganismCode.y))
uniquesmelt <- unique(checksmeltdiet$FishTagID) # 90 fish IDs missing in catch table

### Actual Join

alldataDiet0 <- full_join(alldata, diet_clean, by = c("FishTagID", "OrganismCode"))
alldataDiet <- filter(alldataDiet0, !is.na(SampleID))
alldataDiet$QAQCBy <- as.character(alldataDiet$QAQCBy)
alldataDiet$Gear <- as.character(alldataDiet$Gear)
alldataDiet$Race.y <- as.character(alldataDiet$Race.y)

alldataDiet$SampleTime.x <- format(alldataDiet$SampleTime.x, "%H:%M:%S")
alldataDiet$SampleDate.x <- format(alldataDiet$SampleDate.x, "%m/%d/%Y")
alldataDiet$SampleTime.y <- format(alldataDiet$SampleTime.y, "%H:%M:%S")
alldataDiet$SampleDate.y <- format(alldataDiet$SampleDate.y, "%m/%d/%Y")
str(alldataDiet)

str(diet_clean)
noSampleID <- filter(alldataDiet, is.na(SampleID))
```

9. Filter for plus count
```{r PlusCount}
plusCount <- alldata %>%
  filter(Plus.Count == "TRUE",
         !is.na(SampleDate)) %>%

  mutate(Species = ifelse(OrganismCode == "SNF", "Centrarchidae",
                  ifelse(OrganismCode == "SCP", "Cottidae",
                    ifelse(OrganismCode == "CAT", "Ictaluridae",
                    ifelse(OrganismCode == "SME", "Osmeridae",
                    ifelse(OrganismCode == "LAM", "Lampetra",
                    ifelse(OrganismCode == "BAS", "Micropterus",
                                        as.character(Species))))))),
         Genus = ifelse(OrganismCode == "SNF", "Perciformes",
                ifelse(OrganismCode == "SCP", "Cottoidei",
                ifelse(OrganismCode == "CAT", "Siluriformes",
                ifelse(OrganismCode == "SME", "Osmeriformes",
                ifelse(OrganismCode == "LAM", "Petromyzontidae",
                ifelse(OrganismCode == "BAS", "Centrarchidae",
                                        as.character(Genus)))))))) %>%
  dplyr::select(c("SampleID", "SampleDate", "SampleTime", "StationCode", "Station.Number", "SampleMethod", "GearID", "GearConditionCode", "VegetationRank", "TrapStatus", "Rev.Counter", "Region", "SeineLength", "SeineWidth", "SeineDepth", "VolumeSeined", "HabitatType", "SubstrateCode", "FieldComments", "DataCorrectionComments", 
"OrganismCode", "Species", "Genus", "Count", 
"FishIDComments")) %>%
    mutate_if(is.factor, as.character) %>%
  mutate_at(vars(StationCode: FishIDComments), ~replace_na(., "")) %>%
  rename(LowestTaxon = Species,
         Parent = Genus,
         SamplingArea = Station.Number)
plusCount$SampleTime <- format(plusCount$SampleTime, "%H:%M:%S")
plusCount$SampleDate <- format(plusCount$SampleDate, "%m/%d/%Y")

today = today()
write.csv(plusCount, paste0("R_write/Fishdata_pluscount_", today, ".csv"))

```

10. Filter for count, create column for no catch
* Add FishTagIDs for each data type
* Edit the species whose lowest taxa are not genus species
```{r Count}
countCatch <- alldata %>%
  filter(Plus.Count != "TRUE",
         !is.na(SampleDate),
         !is.na(SampleTime)) %>%
  mutate(NoCatch = ifelse(OrganismCode == "NONE", "Y", "N"),
         FishTagID2 = FishTagID,
         FishTagID3 = FishTagID,
         FishTagID4 = FishTagID,
         Species = ifelse(OrganismCode == "SNF", "Centrarchidae",
                  ifelse(OrganismCode == "SCP", "Cottidae",
                    ifelse(OrganismCode == "CAT", "Ictaluridae",
                    ifelse(OrganismCode == "SME", "Osmeridae",
                    ifelse(OrganismCode == "LAM", "Lampetra",
                    ifelse(OrganismCode == "BAS", "Micropterus",
                                        as.character(Species))))))),
         Genus = ifelse(OrganismCode == "SNF", "Perciformes",
                ifelse(OrganismCode == "SCP", "Cottoidei",
                ifelse(OrganismCode == "CAT", "Siluriformes",
                ifelse(OrganismCode == "SME", "Osmeriformes",
                ifelse(OrganismCode == "LAM", "Petromyzontidae",
                ifelse(OrganismCode == "BAS", "Centrarchidae",
                                        as.character(Genus)))))))) %>%
dplyr::select(c("SampleID", "SampleDate", "SampleTime", "StationCode", "Station.Number", "SampleMethod", "GearID", "GearConditionCode", "VegetationRank", "TrapStatus", "Rev.Counter", "Region", "SeineLength", "SeineWidth", "SeineDepth", "VolumeSeined", "HabitatType", "SubstrateCode", "FieldComments", "DataCorrectionComments", "NoCatch",
"OrganismCode", "Species", "Genus", "ForkLength", "TotalLength", "Weight", "Sex",
"Spawning.Condition", "MarkCode", "Race", "StageCode", "Dead", 
"CWTSample", "Genetic.Sample", "Direct.Take", "Indirect.Take", "FishTagID", "Count",
"FishIDComments", "CWT_TagCode", "CWTComments",
"GeneticID1", "Prob1", "GeneticID2", "Prob2", "FishTagID2", "SalmComments",
"numChrom", "V.shape", "GeneticID", "qDS", "qLFS" ,"qWAG", "GenotypeRun", "FishTagID3", "SmeltComments")) %>%
  mutate_if(is.factor, as.character) %>%
  mutate_at(vars(StationCode: SmeltComments), ~replace_na(., "")) %>%
  mutate(TrapStatus = replace(TrapStatus, SampleMethod %in% c("BSEIN", "PSEIN", "FKTR"), ""),
         Rev.Counter = replace(Rev.Counter, SampleMethod %in% c("BSEIN", "PSEIN", "FKTR"), ""),
         Region = replace(Region, SampleMethod != "BSEIN", ""),
         SeineLength = replace(SeineLength, SampleMethod != "BSEIN", ""),
         SeineWidth = replace(SeineWidth, SampleMethod != "BSEIN", ""),
         SeineDepth = replace(SeineDepth, SampleMethod != "BSEIN", ""),
         VolumeSeined = replace(VolumeSeined, SampleMethod != "BSEIN", ""),
         HabitatType = replace(HabitatType, SampleMethod != "BSEIN", ""),
         SubstrateCode = replace(SubstrateCode, SampleMethod != "BSEIN", ""),
         CWT_TagCode = replace(CWT_TagCode, !OrganismCode %in% salmonids, ""),
        CWTComments = replace(CWTComments, !OrganismCode %in% salmonids, ""),
        GeneticID1 = replace(GeneticID1, !OrganismCode %in% salmonids, ""),
        GeneticID2 = replace(GeneticID2, !OrganismCode %in% salmonids, ""),
        Prob1 = replace(Prob1, !OrganismCode %in% salmonids, ""),
        Prob2 = replace(Prob2, !OrganismCode %in% salmonids, ""),
        SalmComments = replace(SalmComments, !OrganismCode %in% salmonids, ""),
        numChrom = replace(numChrom, !OrganismCode %in% smelts, ""),
        V.shape = replace(V.shape, !OrganismCode %in% smelts, ""),
        GeneticID = replace(GeneticID, !OrganismCode %in% smelts, ""),
        qDS = replace(qDS, !OrganismCode %in% smelts, ""),
        qLFS = replace(qLFS, !OrganismCode %in% smelts, ""),
        qWAG = replace(qWAG, !OrganismCode %in% smelts, ""),
        GenotypeRun = replace(GenotypeRun, !OrganismCode %in% smelts, ""),
        SmeltComments = replace(SmeltComments, !OrganismCode %in% smelts, "")) %>%
  rename(LowestTaxon = Species,
         Parent = Genus,
         SamplingArea = Station.Number) %>%
  arrange(OrganismCode)



# Time formatting 
countCatch$SampleTime <- format(countCatch$SampleTime, "%H:%M:%S")
countCatch$SampleDate <- format(countCatch$SampleDate, "%m/%d/%Y")

# Filter out count > 1
countCatchInd <- filter(countCatch, Count == 1)
countCatchMult <- filter(countCatch, Count != 1)
countCatchMult2 <- countCatchMult[rep(seq_len(dim(countCatchMult)[1]), countCatchMult$Count), ]

# Write files
today <-  today()
write.csv(countCatchInd, paste0("R_write/Fishdata_individual_", today, ".csv"))
write.csv(countCatchMult, paste0("R_write/Fishdata_countnotequalto1_", today, ".csv"))
write.csv(countCatchMult2, paste0("R_write/Fishdata_countnotequalto1Fixed_", today, ".csv"))

summary(countCatchInd)
checkCHN <- filter(countCatch, OrganismCode == "CHN")
```

11. NAs
```{r na}
nas <- alldataDiet %>%
  filter(is.na(Plus.Count))
```

12. Filter for FishTagIds within diet file.
Write file.
```{r Diet file}
DietIDs <- unique(diet_clean$FishTagID)

Diet <- alldataDiet %>% 
  filter(FishTagID %in% DietIDs) %>%
  select(c( "SampleID", "SampleDate.x", "SampleTime.x", "StationCode.x", "SampleMethod", "OrganismCode", "Race.x", "ForkLength.x", "Weight.x", "SampleDate.y", "SampleTime.y", "StationCode.y", "Gear","Race.y",
"ForkLength.y", "ForkLengthLabel", "Weight.y", "WeightLabel", "Fullness", "Digestion", 
"WeightStomachFull", "WeightStomachEmpty", "PreyTaxa", "LifeStage", "HigherTaxa",
"Count.y", "WeightPrey", "StomachBrokenDamaged", "StomachComments",
"ProcessedBy", "QAQCBy", "FishTagID")) %>%
  mutate_if(is.factor, as.character) %>%
  mutate_at(vars(SampleID: FishTagID), ~replace_na(., "")) %>%
  mutate(SampleDate.y = replace(SampleDate.y, !OrganismCode %in% dietOrgs, ""),
       SampleTime.y = replace(SampleTime.y, !OrganismCode %in% dietOrgs, ""),
       StationCode.y = replace(StationCode.y, !OrganismCode %in% dietOrgs, ""),
       Gear = replace(Gear, !OrganismCode %in% dietOrgs, ""),
       Race.y = replace(Race.y, !OrganismCode %in% dietOrgs, ""),
        ForkLength.y = replace(ForkLength.y, !OrganismCode %in% dietOrgs, ""),
        ForkLengthLabel = replace(ForkLengthLabel, !OrganismCode %in% dietOrgs, ""),
        Weight.y = replace(Weight.y, !OrganismCode %in% dietOrgs, ""),
        WeightLabel = replace(WeightLabel, !OrganismCode %in% dietOrgs, ""),
        Fullness = replace(Fullness, !OrganismCode %in% dietOrgs, ""),
        Digestion = replace(Digestion, !OrganismCode %in% dietOrgs, ""),
        WeightStomachFull = replace(WeightStomachFull, !OrganismCode %in% dietOrgs, ""),
        WeightStomachEmpty = replace(WeightStomachEmpty, !OrganismCode %in% dietOrgs, ""),
        PreyTaxa = replace(PreyTaxa, !OrganismCode %in% dietOrgs, ""),
        LifeStage = replace(LifeStage, !OrganismCode %in% dietOrgs, ""),
        HigherTaxa = replace(HigherTaxa, !OrganismCode %in% dietOrgs, ""),
        Count.y = replace(Count.y, !OrganismCode %in% dietOrgs, ""),
        WeightPrey = replace(WeightPrey, !OrganismCode %in% dietOrgs, ""),
        StomachBrokenDamaged = replace(StomachBrokenDamaged, !OrganismCode %in% dietOrgs, ""),
        ProcessedBy = replace(ProcessedBy, !OrganismCode %in% dietOrgs, ""),
        QAQCBy = replace(QAQCBy, !OrganismCode %in% dietOrgs, ""),
        StomachComments = replace(StomachComments, !OrganismCode %in% dietOrgs, ""))  %>%
  rename(SampleDate = SampleDate.x,
         SampleTime = SampleTime.x,
         StationCode = StationCode.x,
         ForkLength = ForkLength.x,
         Weight = Weight.x,
         Race = Race.x,
         SampleDate.diet = SampleDate.y,
         SampleTime.diet = SampleTime.y,
         StationCode.diet = StationCode.y,
         Gear.diet = Gear,
         ForkLength.diet = ForkLength.y,
         Weight.diet = Weight.y,
         Race.diet = Race.y,
    PreyCount = Count.y)

# Change time format
Diet$SampleTime <- format(Diet$SampleTime, "%H:%M:%S")
Diet$SampleDate <- format(Diet$SampleDate, "%m/%d/%Y")

summary(Diet)

# Write files
today <-  today()
write.csv(Diet, paste0("R_write/Diet_", today, ".csv"))
```



```{r plotcheck}
countCatch2 <- countCatch %>%
  mutate(month = month(SampleDate),
         year = year(SampleDate))
countCatch2a <- countCatch2 %>%
  group_by(year, month, OrganismCode) %>%
  summarize(mean.count =mean(Count))

ggplot(countCatch2a, aes(x = year, y = mean.count, fill = OrganismCode)) + geom_bar(stat = "identity")
ggplot(countCatch2a, aes(x = month, y = mean.count, fill = OrganismCode)) + geom_bar(stat = "identity")
```

